Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-27 paper_jasa.tex
data summary table modified

\green{Would it make sense to expand this table now to show number of lineups for different experimental conditions?? Maybe not}
\begin{table}[hbtp]
\caption{Number of subjects, gender and total lineups for all three experimental data sets. Note that in some of the lines the number of male and female participants does not add up to the total number of participants due to missing demographic information. }
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
 & \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\ \cline{2-5}  \cline{6-9}   \cline{10-13}
 & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
   & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 & 156 & 106 &  50 & 1681 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

>>>>

\green{Would it make sense to expand this table now to show number of lineups for different experimental conditions?? Maybe not}
\begin{table}[hbtp]
\caption{Number of subjects, gender and total lineups for all three experimental data sets. Note that in some of the lines the number of male and female participants does not add up to the total number of participants due to missing demographic information. }
\begin{center}
\begin{tabular}{ccrrcc}
   \hline 
 Experiment & Subject & Male & Female & Total &Lineup\\ 
    \hline
  1 & 239 & 121 & 107 & 2317 & 60 \\ 
  2 & 351 & 185 & 164 & 3858 & 70 \\ 
  3 & 156 & 106 &  50 & 1681 & 30 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}
